
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{chngpage}
%\usepackage{bigints}

\usepackage{vmargin}
% left top textwidth textheight headheight
% headsep footheight footskip
\setmargins{2.0cm}{2.5cm}{16 cm}{22cm}{0.5cm}{0cm}{1cm}{1cm}
\renewcommand{\baselinestretch}{1.3}

\setcounter{MaxMatrixCols}{10}
\begin{document}

%=====================================================%
  % - Question 2
%Probability Distributions

\begin{enumerate}



\item A semi-professional basketball team has a first-team squad of fifteen out-field players.
On any given week during the playing season, there is a 5\% chance that a player will receive an injury.
\begin{enumerate}[(a)]
\item  What is the probability that there will be no injuries?
  \item  What is the probability that there will be exactly one injured player?
  \item  What is the probability that there will be three or more injured players?
  \end{enumerate}
\smallskip 
\item Suppose that the prevalence of a genetic condition is new-born children is 1 in 5,000 births. Suppose that the maternity hospitals in Munster typically will have 10,000 live births in any given year.\\ 
Use an appropriate approximation method to estimate the the probability of the following events.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Poisson Approximation (7 Marks)
\begin{itemize}
\item[(a)]  State the approximation method that you will use, and show that this approach is valid in this instance.
\item [(b)] There will be no occurrences of the genetic condition in newborn children for a given year.
\item [(c)] There will be exactly one occurrence of the genetic condition in newborn children for a given year.
\item [(d)] There will be two or more occurrences of the genetic condition in newborn children for a given year.
\end{itemize}


\end{enumerate}

%=====================================================%
\end{document}
