
\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{multicol}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{MathsResource} \chead{Calculus - Partial Derivatives} \rhead{Tutorial Sheets} %\input{tcilatex}
\begin{document}


\subsection*{Sequences and Series - Tutorial 2}

\begin{enumerate}
	\item 
	The second term $u_2$ of a geometric sequence is 4. The fifth term $u_5$ is -32. \\  Answer the following questions. Both questions are worth 2 Marks each.
	\begin{itemize}
		\item[(a)] Find the common ratio $r$. 
		\item[(b)] Find the third and sixth term $u_3$ and $u_6$.
	\end{itemize}
	

	
	\item 	Three consecutive terms of an arithmetic series are 
	\[4x+3,\;\;6x-8,\;\;8x-19.\]
	Find the values for $x$ and constant difference $d$.
	%answer is 460
	
		
		
	\item Express the following repeating decimal number as a simple fraction. Show your workings.
	
	\[0.243243243243243....\]

	
		\item  Express the following repeating decimal number as a simple fraction. Show your workings.
		
		\[0.513513513513....\]
		
		
		\item What does the following sequence converge to?
	\[ u_n  = \frac{n+3}{4n+2}\]
	
	%------------------------%
	%%updated for 2016
	\item  Suppose that the following term is the general term for a series. Use the Ratio Test to test this series for convergence
	
	\[u_n=\frac{2^n}{n!}\]
	
	
	
	%------------------------%
	%%updated for 2016
	\item  Find the sum of the telescoping series  \[ \sum^{\infty}_{n=1} \frac{2
		}{(2n-1)(2n+1)}\]
	

		\item  Find the sum of the following telescoping series
		\[  \sum^{\infty}_{n=1}   \frac{6}{(3n+1)(3n+4)}  \]
		



%=====================================================%
%% - Horizontal and Vertical Asymptotes
%% - http://media.wix.com/ugd/70b98b_39a909a40ea3098062c0bebfb4304ed6.pdf
%% - READY	
		\item  Suppose the general term $u_n$ is given as  $u_n = \displaystyle{\frac{3^n}{n! \times n!} } .$.State $u_{n+1}$ and hence calculate a simplified expression for $r$, where 
		{
			\large
		$\displaystyle{ r = \frac{u_{n+1}}{u_n} }$.
		}



\end{enumerate}
\end{document}
