%% MR_LinearAlgebra_Tutorial_7_LinearEquations.pdf
%% https://www.amazon.com/clouddrive/share/L2TdRTObXydeQjIzjkyGFrIFCWvTV25uB3VZE51XnTK
%%

\documentclass[12pt, a4paper]{report}

\usepackage{epsfig}
\usepackage{subfigure}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{subfiles}
\usepackage{framed}
\usepackage{subfiles}
\usepackage{amsthm, amsmath}
\usepackage{amsbsy}
\usepackage{framed}
\usepackage[usenames]{color}
\usepackage{listings}
\lstset{% general command to set parameter(s)
basicstyle=\small, % print whole listing small
keywordstyle=\color{red}\itshape,
% underlined bold black keywords
commentstyle=\color{blue}, % white comments
stringstyle=\ttfamily, % typewriter type for strings
showstringspaces=false,
numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt, %
frame=shadowbox,
rulesepcolor=\color{black},
,columns=fullflexible
} %
%\usepackage[dvips]{graphicx}
\usepackage{natbib}
\bibliographystyle{chicago}
\usepackage{vmargin}

\renewcommand{\baselinestretch}{1.5}
\pagenumbering{arabic}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{ill}[theorem]{Example}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{axiom}{Axiom}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{notation}{Notation}
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]
\newtheorem{example}{Example}[section]
\renewcommand{\thenotation}{}
\renewcommand{\thetable}{\thesection.\arabic{table}}
\renewcommand{\thefigure}{\thesection.\arabic{figure}}
\title{Research notes: linear mixed effects models}
\author{ } \date{ }


\begin{document}
\begin{enumerate}
    \item Write down the coefficient matrix of the following homogeneous system of equations and then solve the system of equations: 


\begin{align*}
x_1 + 2x_2 &= 0\\
x_1 + x_2 - 2x_3 &= 0\\
x_2 + 2x_3 &= 0.
\end{align*}

\item  Consider the linear system of equations 
\begin{align*}
x_1 + 2x_2 &= 6\\
x_1 + 2x_2 - 2x_3 &= 8\\
x_2 + 2x_3 &= -2.
\end{align*}
\begin{enumerate}[(i)]
\item Write down the augmented matrix of this system. 
\item Does this system of equations have a unique solution? Justify your answer. 
\item  Solve the system of equations, using any appropriate method. 
\end{enumerate}
\item  Consider the linear system
\begin{align*}
x_1 + x_3 &= 4\\
2x_1 + 4x_2 + x_3 &= -3\\
x_2 + 3x_3 &= 7.
\end{align*}
\begin{itemize}
\item[(i)] Write down the coefficient matrix and the augmented matrix of this system.  %\marks{4}

\item[(ii)]  What can you say about the solution set of the system? Justify your answer. %\marks{4}

\item[(ii)] Solve the system of equations, using any appropriate method. Show your workings for each stage of the calculation.
\end{itemize}
%\item Consider the homogeneous system:
%\begin{align*}
%x_1 + x_3 &= 0\\
%2x_1 + 4x_2 + x_3 &= 0\\
%x_2 + 3x_3 &= 0.
%\end{align*}
%What can you say about its solution set?%\marks{4}




\end{enumerate}
\end{document}
